### 2006-05-06 inst/paper/paper2.tex
Changed paper 2 to match the new classes.  Also updated some of the man pages.
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MVCClass@17887 bc3139a8-67e5-0310-9ffc-ced21a209358

\bibliographystyle{amsplain}
\bibliography{paper2}

\begin{titlepage}
\begin{center}
\Large
\vspace*{1in}
\textbf{Creating Linked, Interactive Views to \linebreak Explore Linked Data} \\
\vspace{1in}
\textbf{Dana-Farber Cancer Institute}\\ 
\textbf{February 2, 2006} \\
\vspace{1in} 
\textbf{Elizabeth Whalen} \\
\end{center}
\end{titlepage}
\normalsize
\newpage

@@

As shown in Figure \ref{Fig:EventFun}, the slots in the \Rclass{gEventFun}
class are \Rslot{callFun}, \Rslot{shortName}, and \Rslot{preprocessFun}.  The
\Rslot{callFun} slot is the name of the callback function, the
\Rslot{shortName} slot is a short description of the function, and the
\Rslot{preprocessFun} slot is a character vector of all preprocessing
functions that must be called before the callback function.

@@

As shown in Figure \ref{Fig:MVCClass}, the \Rclass{MVC} class has five slots
which are, \Rslot{model}, \Rslot{viewList}, \Rslot{controller},
\Rslot{parentMVC}, and \Rslot{childMVCList}.  The \Rslot{model} slot stores
the model object, the \Rslot{viewList} slot is a list of the
view objects for this model, the \Rslot{controller} slot is an
environment that stores information for this \Robject{MVC}, the
\Rslot{parentMVC} slot is the name of the parent model
(\Robject{MVC}), and the \Rslot{childMVCList} slot is a list of the children
models (\Robject{MVCs}).  Note that model and
\Robject{MVC} objects use the same name so the \Rslot{parentMVC} slot refers
to both the name of the model and the name of the \Robject{MVC}.
Similarly, for the \Rslot{childMVCList} slot, the names in the list refer to
both the name of the model and the name of the \Robject{MVC}.

\begin{figure}[ht]
  \begin{center}
    \scalebox{0.6}{\includegraphics{MVCClass.jpg}}
    \caption{ The MVC Class. }
    \label{Fig:MVCClass}
  \end{center}
\end{figure}

Thus, the \Rclass{MVC} class not only binds the model,
view, and controller objects together, but it also shows
that the \Robject{MVC} objects are related to each other through a
parent-child (tree) hierarchy, as shown in Figure \ref{Fig:Hier}.  In this
picture, `model1' is the name of the original \Robject{MVC} object (model) and
from it, two \Robject{MVC} objects were created, `model2.1' and
`model2.2'. Then from `model2.1', three \Robject{MVC} objects were created,
`model3.1', `model3.2', and `model3.3'.  As an example, model1 could be gene
expression data, model2.1 could be gene expression data that is a subset of
model1 (based on filtering), model2.2 could be derived by performing
multidimensional scaling (MDS) on model1, model 3.1 could be the gene ontology
(GO) graph representing the molecular functions of the genes in model2.1,
model 3.2 could be the KEGG pathways that the genes in model2.1 are involved
in, and model 3.3 could be the chromosome locations of the genes in model2.1.

@@

\begin{figure}[ht]
  \begin{center}
    \scalebox{0.6}{\includegraphics{MessageClass.jpg}}
    \caption{ Inheritance for Message Objects. }
    \label{Fig:Mess}
  \end{center}
\end{figure}

@@

Currently, there are two types of messages for messaging within a
model, view, controller object: an add and an update message.  Both the add
message, \Rclass{gAddMessage}, and the update message, \Rclass{gUpdateMessage},
contain three slots, \Rslot{dataName}, \Rslot{mData}, and \Rslot{type}.
\Rslot{dataName} is the character string that gives the name of the model,
\Rslot{mData} is a list of data needed to perform the addition or alteration
operation, and \Rslot{type} is a character string that gives the type of
addition or alteration to perform.  Both \Rclass{gAddMessage} and
\Rclass{gUpdateMessage} are virtual classes.

Since adding a view requires different information and methods from adding a
model (and similarly with updating views versus models), it makes sense to
have two separate message classes for these operations.  Messages
sent between components are from one of the following classes:
\Rclass{gAddDataMessage}, \Rclass{gAddViewMessage},
\Rclass{gUpdateDataMessage}, and \Rclass{gUpdateViewMessage}.  The
\Rclass{gAddDataMessage} class represents a message to add a model
and a \Robject{MVC} object because whenever a model is added, a
\Robject{MVC} object is created that contains this model.  The
\Rclass{gAddViewMessage} class represents a message to create a view.  This
message can only be used after a model has been added.

@@

>>>>

\bibliographystyle{amsplain}

\begin{titlepage}
\begin{center}
\Large
\vspace*{1in}
\textbf{Creating Linked, Interactive Views to \linebreak Explore Linked Data} \\
\vspace{1in}
\textbf{Dana-Farber Cancer Institute}\\ 
\textbf{May 6, 2006} \\
\vspace{1in} 
\textbf{Elizabeth Whalen} \\
\end{center}
\end{titlepage}
\normalsize
\newpage

@@

As shown in Figure \ref{Fig:EventFun}, the slots in the \Rclass{gEventFun}
class are \Rslot{callFun}, \Rslot{shortName}, and \Rslot{preprocessFun}.  The
\Rslot{callFun} slot is the callback function, the
\Rslot{shortName} slot is a short description of the function that
identifies the callback function, and the
\Rslot{preprocessFun} slot is a list of all preprocessing
functions that must be called before the callback function.

@@

As shown in Figure \ref{Fig:MVCClass}, there is a virtual class, \Rclass{MVC},
that binds the MVC inheritance structure together.  The virtual class,
\Rclass{MVC}, has three slots, which are \Rslot{model}, \Rslot{viewList}, and
\Rslot{controller}.  The \Rslot{model} slot stores the model object, the
\Rslot{viewList} slot is a list of the view objects for this model, and the
\Rslot{controller} slot is an environment that stores information for this
\Robject{MVC}.  These three pieces of information are needed to bind the
model, view, and controller into one object.  To create instances of a single
MVC, the \Rclass{singleModelMVC} class, which inherits from the virtual
\Rclass{MVC} class, can be used.

Inheriting from the \Rclass{singleModelMVC} class is the
\Rclass{linkedModelMVC} class, which represents a \Robject{MVC} object that
can be linked to other \Robject{MVC} objects.  The \Rclass{linkedModelMVC}
class has two additional slots: \Rslot{parentMVC}, which is the name of the
parent model (\Robject{MVC}), and \Rslot{childMVCList}, which is a list of the
child models (\Robject{MVCs}).  Note that model and
\Robject{MVC} objects use the same name so the \Rslot{parentMVC} slot refers
to both the name of the model and the name of the \Robject{MVC}.
Similarly, for the \Rslot{childMVCList} slot, the names in the list refer to
both the name of the model and the name of the \Robject{MVC}.  In this paper,
we are assuming that models are linked so all \Robject{MVC} objects are of
class \Rclass{linkedModelMVC}.

\begin{figure}[ht]
  \begin{center}
    \scalebox{0.6}{\includegraphics{fullMVCClass.jpg}}
    \caption{ The MVC Class. }
    \label{Fig:MVCClass}
  \end{center}
\end{figure}

Thus, the \Rclass{linkedModelMVC} class not only binds the model,
view, and controller objects together, but it also shows
that the \Robject{linkedModelMVC} objects are related to each other through a
parent-child (tree) hierarchy, as shown in Figure \ref{Fig:Hier}.  In this
picture, `model1' is the name of the original \Robject{MVC} object
(model) and from it, two \Robject{MVC} objects were created,
`model2.1' and `model2.2'. Then from `model2.1', three
\Robject{MVC} objects were created, `model3.1', `model3.2', and
`model3.3'.  As an example, model1 could be gene 
expression data, model2.1 could be gene expression data that is a subset of
model1 (based on filtering), model2.2 could be derived by performing
multidimensional scaling (MDS) on model1, model 3.1 could be the gene ontology
(GO) graph representing the molecular functions of the genes in model2.1,
model 3.2 could be the KEGG pathways that the genes in model2.1 are involved
in, and model 3.3 could be the chromosome locations of the genes in model2.1.

@@

\begin{figure}[ht]
  \begin{center}
    \scalebox{0.6}{\includegraphics{newMessageClass.jpg}}
    \caption{ Inheritance for Message Objects. }
    \label{Fig:Mess}
  \end{center}
\end{figure}

@@

Currently, there are two types of messages for messaging within a
model, view, controller object: an add and an update message.  These two types
of messages are both performing some type of modification and thus, both the
add message, \Rclass{gAddMessage}, and the update message,
\Rclass{gUpdateMessage}, inherit from the virtual class,
\Rclass{gModifyMessage}, which contains three slots, \Rslot{dataName},
\Rslot{mData}, and \Rslot{type}.  \Rslot{dataName} is the character string
that gives the name of the model, 
\Rslot{mData} is a list of data needed to perform the addition or alteration
operation, and \Rslot{type} is a character string that gives the type of
addition or alteration to perform.  Both \Rclass{gAddMessage} and
\Rclass{gUpdateMessage} are virtual classes.

Since adding a view requires different information and methods from adding a
model (and similarly with updating views versus models), it makes sense to
have two separate message classes for these elements.  Messages
sent between components are from one of the following classes:
\Rclass{gAddDataMessage}, \Rclass{gAddViewMessage},
\Rclass{gUpdateDataMessage}, and \Rclass{gUpdateViewMessage}.  The
\Rclass{gAddDataMessage} class represents a message to add a model
and a \Robject{MVC} object because whenever a model is added, a
\Robject{MVC} object is created that contains this model.  The
\Rclass{gAddViewMessage} class represents a message to create a view.  This
message can only be used after a model has been added.

@@

\bibliography{paper2}
